`flippant` --- An `R` package for the automated analysis of dithionite scramblase

### 2016-07-19 inst/manuscript/manuscript.rmd
capitalized Bioconductor

# Availablility and Implementation
`flippant` has been implemented in `R` [@r_core_team_r:_2016] and integrated 
into the `bioconductor` collection of tools for biomedical data analysis [@huber_orchestrating_2015]. It is thus install-- and loadable as follows from 
within a functional `R` environment:

>>>>

# Availablility and Implementation
`flippant` has been implemented in `R` [@r_core_team_r:_2016] and integrated 
into the `Bioconductor` collection of tools for biomedical data analysis [@huber_orchestrating_2015]. It is thus install-- and loadable as follows from 
within a functional `R` environment:
